\normalfont \normalsize \huge Battle of Online and Offline Consumption: \\ Comparative Analysis of Amazon and Walmart Stocks

### 2017-06-18 Paper.tex
except prediction

Comparing the volatility of the log return series of Amazon and Walmart from 2010 to 2016, we can find that Amazon’s volatility is higher and more volatile than that of Walmart. This could probably be explained by two alternative reasons. The first one is that the expectation of Amazon's stock may be stronger than that of Walmart. Stock prices reflect the expected value of a firm. The more frequent the change of the expectation of a firm's future value, the more volatile the firm's stock price and thus the more volatile the stock's return. People hold a stronger expectation of Amazon’s future value and adjust their expectation more often. As a result, the price and return of Amazon's stock is more volatile. Figure \ref{price} shows the stock prices of Amazon and Walmart from 2010 to 2016. We can see that the stock price of Amazon has surged sharply from 2010 to 2017. The stock price of Amazon is below 200 at the beginning of the year 2010 but around 800 at the end of the year 2016. However, the stock price of Walmart has not risen that much. At the beginning of the year 2010, it is between 40 and 50 and at the end of the year 2016, it is around 70. The highest appeared in 2015, which is around 80.

@@

%%%%%%%%%%%%%%%%%%%%%%   Prediction   %%%%%%%%%%%%%%%%%%%%%%%
\section{Prediction}
Table \ref{predict} shows the mean and volatility forecasts for the daily log return of Amazon and Walmart. The volatility denotes the conditional standard deviation. As for the stock of Walmart, when the forecast horizon goes to infinity, the return will converge to 0.137\% and the volatility will converge to 2.087795. As for the stock of Walmart, when the forecast horizon goes to infinity, the return will converge to 0.024\% and the volatility will converge to 1.0338010.

\begin{figure}[!htbp]
\begin{minipage}[!htbp]{0.5\linewidth}
\centering
\includegraphics[scale = 0.45]{img/predict_AMZN}
\end{minipage}
\begin{minipage}[!htbp]{0.5\linewidth}
\centering
\includegraphics[scale = 0.45]{img/predict_WMT}
\end{minipage}
\caption{Prediction of Volatility of AMZN and WMT}
\label{predict}
\end{figure}
\newpage

Finally, to forecast the volatility of AMZN stock, we can use the volatility equation $\sigma_t^2 = 1.02+0.129a_{t-1}^2+0.637\sigma_{t-1}^2$. The 1-step-ahead forecast is then $\sigma_{h+1}^2 = 1.02+0.129a_h^2+0.637\sigma_h^2$, where $a_h$ is the residual of the mean equation at time $h$ and $\sigma_h$ is obtained from the volatility equation. For multistep-ahead forecasts, we substitute our forecasts recursively. Table \ref{fc_amzn} shows some mean and volatility forecasts for the AMZN stock. Here, the unit for Log Return is \%.

@@

%%%%%%%%%%%%%%%%%%%%%%   Appendix   %%%%%%%%%%%%%%%%%%%%%%%
\section{Appendix}

>>>>

Comparing the volatility of the log return series of Amazon and Walmart from 2010 to 2016, we can find that Amazon's volatility is higher and more volatile than that of Walmart. This could probably be explained by two alternative reasons. The first one is that the expectation of Amazon's stock may be stronger than that of Walmart. Stock prices reflect the expected value of a firm. The more frequent the change of the expectation of a firm's future value, the more volatile the firm's stock price and thus the more volatile the stock's return. People hold a stronger expectation of Amazon’s future value and adjust their expectation more often. As a result, the price and return of Amazon's stock is more volatile. Figure \ref{price} shows the stock prices of Amazon and Walmart from 2010 to 2016. We can see that the stock price of Amazon has surged sharply from 2010 to 2017. The stock price of Amazon is below 200 at the beginning of the year 2010 but around 800 at the end of the year 2016. However, the stock price of Walmart has not risen that much. At the beginning of the year 2010, it is between 40 and 50 and at the end of the year 2016, it is around 70. The highest appeared in 2015, which is around 80.

@@

%%%%%%%%%%%%%%%%%%%%%%   Prediction   %%%%%%%%%%%%%%%%%%%%%%%
\section{Prediction}
Table \ref{predict} shows the mean and volatility forecasts for the daily log return of Amazon and Walmart. The volatility denotes the conditional standard deviation. As for the stock of Walmart, when the forecast horizon goes to infinity, the return will converge to 0.14\% and the volatility will converge to 2.09. As for the stock of Walmart, when the forecast horizon goes to infinity, the return will converge to 0.02\% and the volatility will converge to 1.03.

\begin{figure}[!htbp]
\begin{minipage}[!htbp]{0.5\linewidth}
\centering
\includegraphics[scale = 0.45]{img/predict_AMZN}
\end{minipage}
\begin{minipage}[!htbp]{0.5\linewidth}
\centering
\includegraphics[scale = 0.45]{img/predict_WMT}
\end{minipage}
\caption{Prediction of Volatility of AMZN and WMT}
\label{predict}
\end{figure}

Finally, to forecast the volatility of AMZN stock, we can use the volatility equation $\sigma_t^2 = 1.02+0.129a_{t-1}^2+0.637\sigma_{t-1}^2$. The 1-step-ahead forecast is then $\sigma_{h+1}^2 = 1.02+0.129a_h^2+0.637\sigma_h^2$, where $a_h$ is the residual of the mean equation at time $h$ and $\sigma_h$ is obtained from the volatility equation. For multistep-ahead forecasts, we substitute our forecasts recursively. Table \ref{fc_amzn} shows some mean and volatility forecasts for the AMZN stock. Here, the unit for Log Return is in percentage (\%).

@@
